Sketch Recognition and Understanding

### 2009-08-04 draft/System.tex

\subsubsection{Polygon Division Algorithm \textsl{AlgS1}}
\label{sec:PolygonDivisionAlgorithm}
The first algorithm, the algorithm tries to segment the stroke as a polygon. The final solution is a set of line segments that best define the input stroke. Given the inputs stroke let's define the set of points in the stroke as  $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ which is the set of consecutive points from start of stroke till the end. The arc $\widehat{x_ix_j}$ is defined as the consecutive set of points from point $x_i,x_{i+1} \cdots,x_j$. The line
$\overline{x_i x_j} $ is the straight line connecting point $x_i$ to point $x_j$. The approximation error is computed by the equation \ref{eq:ErrorSwarm1} 
\begin{equation}
E=\sum\nolimits_{i = 0}^M e ( \widehat{x_ix_{i+1}},\overline{x_i x_{i+1}})
\label{eq:ErrorSwarm1}
\end{equation}
 where $M$ is the number of dominant points in this solution.  The error $ e ( \widehat{x_ix_j},\overline{x_i x_j})$ is computed as the sum of squared perpendicular distance from every point along the arc $\widehat{x_ix_j}$ to the line $\overline{x_i x_j}$ \cite{PolygonApproximationPSO}. Figure \ref{fig:DPSOERROR} shows a graphical representation of the error. The fitness is computed using equation \ref{eq:fitnessSwarm1} 
\begin{equation}
\max fitness(p_i ) = \left\{ {\begin{array}{*{20}c}
   { - E/\varepsilon N} & {ifE > \varepsilon ,}  \\
   {D/\sum\limits_{j = 1}^N {p_{ij} } } & {otherwise}  \\
\end{array}} \right.
\label{eq:fitnessSwarm1}
\end{equation}%\]
where $N$ is the number of points in the stroke, $D$ is the number of point in the solution that was previously labeled as $P_{pd}$  and $E$ is the computed error and $\varepsilon$ is the error threshold.  If the solution produced an error that exceed the error threshold $\varepsilon$ the fitness function assign a -ve value for the solution to express it's in feasibility, otherwise the inverse of the number of vertex produced is used to access the solution fitness in terms of minimum number of vertices'.  This fitness function optimize two goals the first is to move the solution into the feasible solution space with acceptable error bounds and second is to fly the particle to a new position which may result in a polygon with a fewer number of vertices'\cite{PolygonApproximationPSO}. 
\begin{figure}
	\centering
  \includegraphics[scale=0.8]{images/pso1.eps}			
	\caption{AlgS1 Error}% a) Possible dominant point b) Particle encoding  
	\label{fig:DPSOERROR}
\end{figure}
 %The error is chosen to in favor of larger than the threshold is given a -ve value to lower the value of solution otherwise the system will favor the lower number of vertices'.\\ %we will want to lower the number of vertices'. \\
%if we say that s
%Alg1:
%Alg2: 
\subsubsection{Hybrid Curve Algorithm \textsl{AlgS2}}
\label{sec:PolygonDivisionAlgorithm}

@@

>>>>

\subsubsection{Polygon Division Algorithm \textsl{AlgS1}}
\label{sec:PolygonDivisionAlgorithm}
The first algorithm, the algorithm tries to segment the stroke as a polygon. The final solution is a set of line segments that best define the input stroke. Given the inputs stroke let's define the set of points in the stroke as  $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ which is the set of consecutive points from start of stroke till the end. The arc $\widehat{x_ix_j}$ is defined as the consecutive set of points from point $x_i,x_{i+1} \cdots,x_j$. The line
$\overline{x_i x_j} $ is the straight line connecting point $x_i$ to point $x_j$. The approximation error is computed by the equation \ref{eq:ErrorSwarm1} 
\begin{equation}
E=\sum\nolimits_{i = 0}^M e ( \widehat{x_ix_{i+1}},\overline{x_i x_{i+1}})
\label{eq:ErrorSwarm1}
\end{equation}
 where $M$ is the number of dominant points in this solution.  The error $ e ( \widehat{x_ix_j},\overline{x_i x_j})$ is computed as the sum of squared perpendicular distance from every point along the arc $\widehat{x_ix_j}$ to the line $\overline{x_i x_j}$ \cite{PolygonApproximationPSO}. Figure \ref{fig:DPSOERROR} shows a graphical representation of the error. The fitness is computed using equation \ref{eq:fitnessSwarm1} 
\begin{equation}
\max fitness(p_i ) = \left\{ {\begin{array}{*{20}c}
   { - E/\varepsilon N} & {ifE > \varepsilon ,}  \\
   {D/\sum\limits_{j = 1}^N {p_{ij} } } & {otherwise}  \\
\end{array}} \right.
\label{eq:fitnessSwarm1}
\end{equation}%\]
where $N$ is the number of points in the stroke, $D$ is the number of point in the solution that was previously labeled as $P_{pd}$  and $E$ is the computed error and $\varepsilon$ is the error threshold.  If the solution produced an error that exceed the error threshold $\varepsilon$ the fitness function assign a -ve value for the solution to express it's in feasibility, otherwise the inverse of the number of vertex produced is used to access the solution fitness in terms of minimum number of vertices'.

This fitness function optimize two goals the first is to move the solution into the feasible solution space with acceptable error bounds and second is to fly the particle to a new position which may result in a polygon with a fewer number of vertices'\cite{PolygonApproximationPSO}.  The two optimization goals are pursued simultaneously since the DPSO evolves with swarm particles and each of which may invoke different fitness evaluation depending on the incurred approximation error. 
\begin{figure}
	\centering
  \includegraphics[scale=0.8]{images/pso1.eps}			
	\caption{AlgS1 Error}% a) Possible dominant point b) Particle encoding  
	\label{fig:DPSOERROR}
\end{figure}
 %The error is chosen to in favor of larger than the threshold is given a -ve value to lower the value of solution otherwise the system will favor the lower number of vertices'.\\ %we will want to lower the number of vertices'. \\
%if we say that s
%Alg1:sinc
%Alg2: 
\subsubsection{Hybrid Curve Algorithm \textsl{AlgS2}}
\label{sec:PolygonDivisionAlgorithm}

@@

\section{Step by Step Example}
\label{secstepExample}
In this section a step by step example is presented to clearify the presented sytesm. Let us make an assumption that the user will draw a clock using two strokes. Figure \ref{} show the two stroke and how the user draw them. The next steps demonstrate how ouput of the system after each step

\begin{landscape}
\begin{scriptsize}

%\begin{table}
	%\centering

%\scalebox{0.6}{		
\begin{longtable}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{13cm}|}
	\caption{StepsStroke1}
	\label{tab:StepsStroke1} \\

\hline 
\multicolumn{1}{|p{2cm}|}{\textbf{Step}} & 
\multicolumn{1}{p{2cm}|}{\textbf{Discription}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Inputs}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Details}} &
 \multicolumn{1}{p{13cm}|}{\textbf{Output}} 
\\ \hline 
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\multicolumn{1}{|p{2cm}|}{\textbf{Step}} & 
\multicolumn{1}{p{2cm}|}{\textbf{Discription}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Inputs}} &
 \multicolumn{1}{p{2cm}|}{\textbf{Details}} &
 \multicolumn{1}{p{13cm}|}{\textbf{Output}} 
\\ \hline 
\endhead

%Step & Discription of Step & Input & Steps & Output \\ \hline
Stroke point extraction & Extracting point and computing boundary data & -- &  see Section \ref{} & 
\begin{scriptsize}
Stroke has 62 points = [P(198.0,153.0), P(197.0,150.0), P(197.0,145.0), P(198.0,140.0), P(203.0,125.0), P(205.0,120.0) , P(205.0,117.0), P(210.0,111.0) , P(214.0,103.0) , P(219.0,97.0), P(225.0,89.0) , P(229.0,85.0) , P(242.0,77.0) , P(247.0,73.0) , P(275.0,64.0) , P(287.0,62.0) , P(325.0,62.0) , P(333.0,63.0) , P(362.0,68.0) , P(372.0,72.0) , P(391.0,77.0) , P(406.0,83.0) , P(424.0,91.0) , P(440.0,100.0), P(474.0,133.0) , P(485.0,149.0) , P(492.0,164.0) , P(499.0,182.0) , P(501.0,191.0) , P(501.0,207.0) , P(499.0,222.0) , P(496.0,239.0) , P(471.0,292.0) , P(467.0,302.0) , P(456.0,315.0) , P(441.0,329.0) , P(427.0,339.0) , P(418.0,344.0) , P(398.0,354.0) , P(336.0,371.0) , P(283.0,376.0) , P(263.0,378.0) , P(242.0,378.0) , P(232.0,376.0) , P(213.0,373.0) , P(194.0,367.0) , P(177.0,362.0) , P(138.0,343.0) , P(129.0,336.0) , P(124.0,331.0) , P(120.0,321.0) , P(115.0,310.0) , P(113.0,297.0) , P(112.0,284.0) , P(114.0,256.0) , P(121.0,219.0) , P(128.0,202.0) , P(137.0,184.0) , P(143.0,172.0) , P(154.0,161.0) , P(172.0,146.0) , P(172.0,146.0)]

 Bonding box is  = Corner P(112.0, 62.0), w= 389.0, h=  316.0
 number of point in this stroke is   62
\end{scriptsize}
 \\ \hline
Possible Dominate point Extraction & Computing and for details see Section\ref{} &  Stroke points  & 1. compute   the pdp  &    Number of $P_{dp}$  = 11
 Pdp = [ 2 (197.0 , 145.0 ), 4 (203.0 , 125.0 ), 3 (198.0 , 140.0 ), 22 (424.0 , 91.0 ), 19 (372.0 , 72.0 ), 26 (492.0 , 164.0 ), 28 (501.0 , 191.0 ), 9 (219.0 , 97.0 ), 31 (496.0 , 239.0 ), 0 (198.0 , 153.0 ), 41 (263.0 , 378.0 )]

\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
The circle is   a = 194.5 ,b = 194.5 , Center( 306.5,  220.0 )   with Error =  2.276869953758031 , Percent =0.9093857875960022
 certainty  =  0.1997008626019765 \\ \hline

		\end{longtable}
%}

%\end{table}

\end{scriptsize}

\end{landscape}

%\begin{enumerate}
%\begin{itemize}

%	\item Processing for the first Stroke 1.

%	\item Possible Dominiate Point Extraction
%	\item Segmentation 
%	   Computing 
%	\begin{enumerate}
%	\item Ellipse detection  
%	      Calcualting estimated ellipse with radius = $\frac{w}{2}$  and center as same as the bounding box of stroke.  
%	      The ouput of the system $$
% \end{enumerate}
%	
%	
%\end{enumerate}
%  
%
%\end{itemize}
